---
title: "sample"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

<font size="3">| Variable | Description |</font>
<font size="3">|----------|-------------|</font>
<font size="3">| mpg | Miles/(US) gallon |</font>

1. mpg  -	Miles/(US) gallon
2. cyl  - Number of cylinders                     
3. disp - Displacement (cu.in.) 

<font size="3">1. mpg  -	Miles/(US) gallon</font>
<br>
<font size="3">2. cyl  - Number of cylinders</font>                     

                 


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

